\documentclass{article}

\begin{document}
2.3 Show that in the case of two actions, the softmax operation 
using the Gibbs distribution becomes the logistic, or sigmoid, 
function commonly used in artificial neural networks. What 
effect does the temperature parameter have on the 
function?

\textsc{Solution} The Gibbs distribution for a system with two 
possible actions is given by:
\[
P(a_1) = \frac{e^{-Q(a_1)/\tau}}{e^{-Q(a_1)/\tau} + 
e^{-Q(a_2)/\tau}}
\]
\[
P(a_2) = \frac{e^{-Q(a_2)/\tau}}{e^{-Q(a_1)/\tau} + 
e^{-Q(a_2)/\tau}}
\]

where $Q(a_1)$ and $Q(a_2)$ are the values associated with the two 
actions, and $\tau$ is the temperature parameter.

Now let's define the logistic (sigmoid) function, which is 
commonly used in artificial neural networks. The sigmoid function is 
given by:

\[
\sigma(x) = \frac{1}{1 + e^{-x}}
\]

To show that the softmax operation becomes the logistic (sigmoid) 
function in the case of two actions, let's express $P(a_1)$ in 
terms of the sigmoid function:

\[
P(a_1) = \frac{e^{Q(a_1)/\tau}}{e^{Q(a_1)/\tau} + 
e^{Q(a_2)/\tau}} = \frac{1}{1 + e^{(Q(a_2) - Q(a_1))/\tau}}
\]

Comparing this with the sigmoid function definition, we can see 
that $P(a_1)$ is a sigmoid function with input $-(Q(a_1) - 
Q(a_2) / \tau$:

\[
P(a_1) = \sigma((-(Q(a_1) - Q(a_2)) / \tau)
\]

Thus, we have shown that in the case of two actions, the softmax 
operation using the Gibbs distribution becomes the logistic 
(sigmoid) function commonly used in artificial neural networks.

The temperature parameter $\tau$ has an effect on the softmax 
function as follows:

\begin{enumerate}
\item $\tau \rightarrow 0$, the softmax function becomes more 
"deterministic." The highest-valued action approaches a 
probability of 1, while the others approach 0.
\item When $\tau \rightarrow \infty$, the softmax function 
becomes more "uniform." The probabilities for all actions 
converge to $1/n$, where n is the number of actions. In the case of 
two actions, this means that the probabilities for both actions 
approach 0.5.
\item For intermediate values of $\tau$, the softmax function 
smoothly interpolates between the deterministic and uniform cases, 
producing a balance between exploration and exploitation.
\end{enumerate}

In the context of the sigmoid 
function, the temperature parameter $\tau$ affects the 
steepness of the curve. Higher values of $\tau$ result in a 
flatter curve (smoother transition between 0 and 1), while lower 
values of $\tau$ result in a steeper curve (sharper transition 
between 0 and 1).
\end{document}
